\documentclass[10pt,oneside]{article}
\usepackage{../Resume}

\begin{document}

\hfill\dte\today
\heading
\vspace{\baselineskip}
\vspace{\baselineskip}

Dear Hiring Manager,

\vspace{\baselineskip}

I am writing to apply for the Business Analyst position at the City of Seattle. I am interested in working in the public sector because I am looking for a chance to have a positivie impact on the place I love to call home and it's residents. I believe this BA role would be an excellent fit for my, as I have a good deal of experience both working directly with technology, and with helping lead technology projects to success with end users. Over the last 14 years, I have grown my career from call center and desk side IT support roles to incident management and response. Most recently, though, I have held a Systems Analyst role where I have done extensive data analysis and reporting to all levels of leadership at my organization. The parts of my job I have most consistently enjoyed and excelled at have always been the parts that involve helping filter and illuminate data in order to facilitate informed decision making. I love helping partners and collaborators reach the "a ha" moment where data becomes knowledge and understanding.

\vspace{\baselineskip}

In past jobs, I’ve enjoyed outside-the-box problem solving to make my co-workers jobs, easier by writing and maintaining tools and scripts. At the Service Desk for Nordstrom, for instance, the company lacked a unified hardware asset management tool, so I maintained a PowerShell script that tracked the department’s workstations, laptops and other hardware. More recently, I wrote a small set of bash scripts to help my team automatically export Tableau reports to image files for easy inclusion in a weekly operations meeting that the company’s CTO held. This significantly streamlined our workflow and freed up my team members to focus more energy on non-IT changes in a high-stress timeframe. I created and maintained complex dynamic dashboards for executive assistants, so they could easily and quickly present data to their executives. They found the resources I created to be invaluable timesavers. Finally, In my role as an Incident Manager, I worked closely with the developer team that rolled out our new ServiceNow ticketing system, helping collect and curate user stories, finalize designs, perform user testing, and collect feedback to make the final product something that worked for a wide variety of users' needs.  My passion in my day-to-day work life is building relationships with the people that I work with, and finding ways to collaboratively improve processes. I want to help people make better decisions. I believe these skills and experiences will allow me to be very successful at Seattle IT.

\vspace{\baselineskip}

I am excited for the opportunity to grow my career and skills at the Seattle IT. I am currently volunteering with an organization called Seattle Community Network, which is deploying wireless internet access point for use by underserved communities. It is extremely fulfilling, and I hope to find a job that lines up with my priorities in a similar way. I am eager for the next step of my career to be in alignment with my passions and values; I would love to know more about your team to see if it would be a good fit.

\vspace{\baselineskip}

Thank you for considering me. I hope to hear from you soon.

\vspace{\baselineskip}

Sincerely,

\vspace{\baselineskip}

Michael Shriver

\end{document}
