\documentclass[10pt,oneside]{article}
\usepackage{../Resume}

\begin{document}

\hfill\dte\today
\heading
\vspace{\baselineskip}
\vspace{\baselineskip}

Dear Hiring Manager,

\vspace{\baselineskip}

I am writing to apply for the Incident Response Manager position at Gravity. I've been aware of Gravity and their actions around pay equity and employee satisfaction for several years, and have admired the steps that the company has taken for their workers. Over the last 14 years, I have grown my career from call center and desk side IT support roles to incident management and response. In fact, at Nordstrom I founded the Incident Response Team, and shifted Incident response duties from the Service Desk into its own, dedicated, 24/7 oncall team. I have always thrived in the high-pressure environment that is required to bring all stakeholders together to collaboratively, and quickly, resolve IT Incidents.

\vspace{\baselineskip}

In past jobs, I’ve showed an aptitude for technical communication and collaboration. At the Service Desk at Nordstrom, I was the process owner for IT Incident Management. In that role, I worked closely with product owners across the company to develop a complex, and responsive process that worked well for diverse teams across the organization. Based on that foundation, the Incident Response Team was spun out of the Service Desk into its own team, with me as a core member. More recently, I was tasked with analyzing Incident and Problem Management data in order to provide the top leadership at the company with the information they needed to make critical business decisions for the IT organization. I created and maintained complex dynamic dashboards for executive assistants, so they could easily and quickly present Incident and Problem Management data to their executives. They found the resources I created to be invaluable timesavers. Finally, In my role as an Incident Manager, I worked closely with the developer team that rolled out our new ServiceNow ticketing system, helping collect and curate user stories, finalize designs, perform user testing, and collect feedback to make the final product something that worked for a wide variety of users' needs. During most of this time, I also served as a 24/7 oncall Incident Manager, responding promptly to outages, contacting stakeholders, driving resolution calls and running post-mortem meetings after incident resolution. I believe these skills and experiences will allow me to be very successful in this role.

\vspace{\baselineskip}

I am excited for the opportunity to grow my career and skills at Gravity and I am eager to continue my career working in a field I know well; I would love to know more about your team to see if it would be a good fit.

\vspace{\baselineskip}

Thank you for considering me. I hope to hear from you soon.

\vspace{\baselineskip}

Sincerely,

\vspace{\baselineskip}

Michael Shriver

\end{document}
