\documentclass[10pt,oneside]{article}
\usepackage{../Resume}

\begin{document}

\hfill\dte\today
\heading
\vspace{\baselineskip}
\vspace{\baselineskip}

Dear Hiring Manager,

\vspace{\baselineskip}

I am writing to apply for the Security Awareness & Training Internship at Costco. I am currently enrolled in the Linux and Network Security program at North Seattle College. I am seeking to transition my career from IT Operations Management back to a more technical IT Security focused path. Over the last 14 years, I have grown my career from call center and desk side IT support roles to incident management and response. Most recently, though, I have held a Systems Analyst role where I have done extensive data analysis and reporting to all levels of leadership at my organization. The parts of my job I have most consistently enjoyed and excelled at have been the parts that involve reducing friction between complex computer systems and their users; things like installation and setup, troubleshooting, problem solving, direct support, and documentation. I love to make technology work for people, and I derive satisfaction from making people happy.

\vspace{\baselineskip}

In past jobs, I’ve enjoyed outside-the-box problem solving to make my co-workers jobs easier by writing and maintaining tools and scripts. At the Service Desk for Nordstrom, for instance, the company lacked a unified hardware asset management tool, so I maintained a PowerShell script that tracked the department’s workstations, laptops, and other hardware. More recently, I wrote a small set of bash scripts to help my team automatically export Tableau reports to image files for easy inclusion in a weekly operations meeting with C-suite audience. This significantly streamlined our workflow and freed up my team members to focus more energy on non-IT changes in a high-stress timeframe. I created and maintained complex dynamic dashboards for executive assistants, so they could easily and quickly present data to their executives. They found the resources I created to be invaluable timesavers. Finally, In my role as an Incident Manager, I worked closely with the developer team that rolled out our new ServiceNow ticketing system, helping collect and curate user stories, finalize designs, perform user testing, and collect feedback to make the final product usable for a wide range of needs. I can bring a range of operational and technical experience to the IT Security team, and I will focus all of them on making technology more secure for all Costco staff.

\vspace{\baselineskip}

I am excited for the opportunity to grow my career and skills at Costco. I truly enjoy working with technology, and watching the ways it can break in order to make it more robust. I would love to put those interests into practice in my career. I look forward to learning more about the team and exploring whether I would be a good fit. Thank you for your time and consideration.

\vspace{\baselineskip}

Sincerely,

\vspace{\baselineskip}

Michael Shriver

\end{document}
