\documentclass[10pt,oneside]{article}
\usepackage{../Resume}

\begin{document}m

\hfill\dte\today
\heading
\vspace{\baselineskip}
\vspace{\baselineskip}

Dear Bart.

\vspace{\baselineskip}

I am writing to apply for the IT Specialist position at Gravity. The course of my career so far has taken me from call-center based IT Support roles, to deskside Support roles. From these support roles, I eventually transitioned into Incident Management and response. Most recently, I have held a Systems Analyst role where I have done extensive data crunching and reporting to all levels of leadership at my organization. The parts of my job I have most consistently enjoyed and excelled at have always been the parts that involve complex problem solving and reducing friction that others have with technology.

\vspace{\baselineskip}

I often find myself returning to skills I used in former IT jobs, being the go-to guy for my friends, family, and landlady for all kinds of technical support questions. And I am happy to assist, I love the feeling of helping relieve someone’s frustration with a thorny computer issue. I believe that technology should be about helping people, and people shouldn’t have to spend hours wrestling technology to their will. In past jobs, I’ve enjoyed outside-the-box problem solving to make my job, and the jobs of those around me, easier by writing and maintaining small tools and scripts. At the Service Desk for Nordstrom, for instance, the company lacked a unified hardware asset management tool, so I maintained a powershell script that tracked the department’s workstations, laptops and other hardware. More recently, I wrote a small set of bash scripts to help my current team automatically export Tableau reports to pngs for easy inclusion in a weekly Operations meeting that the company’s CTO held, which streamlined our workflow and freed up my team members to focus more energy on last minute changes in a high-stress timeframe.

\vspace{\baselineskip}

I’m excited for the opportunity to apply at Gravity. I have a friend who works for the company, and I have heard from him that the culture is one of shared goals and appreciation for employees at every level. That level of community strongly matches what I seek in a place of employment. I value open communication, trust, and effective collaboration in my workplace, and I think I would be a great match for your team.

\vspace{\baselineskip}

Thank you for considering me. I hope to hear from you soon.

\vspace{\baselineskip}

Sincerely,

\vspace{\baselineskip}

Michael Shriver

\end{document}
