\documentclass[10pt,oneside]{article}
\usepackage{../Resume}

\begin{document}m

\hfill\dte\today
\heading
\vspace{\baselineskip}
\vspace{\baselineskip}

Dear Austin.

\vspace{\baselineskip}

I am writing to apply for the Deployment Representative position at Gravity. The course of my career so far has taken me from call-center based IT Support roles, to deskside Support roles. From these support roles, I eventually transitioned into Incident Management and response. Most recently, I have held a Systems Analyst role where I have done extensive data crunching and reporting to all levels of leadership at my organization. The parts of my job I have most consistently enjoyed and excelled at have always been the parts that involve complex problem solving and satisfied customers.

\vspace{\baselineskip}

I often find myself returning to skills I used in former customer service jobs, being the go-to guy for my friends, family, and landlady for all kinds of technical support questions. And I am happy to assist, I love the feeling of helping relieve someone’s frustration with a thorny computer issue. I believe that technology should be about helping people, and people shouldn’t have to spend hours wrestling technology to their will. In past jobs, I’ve enjoyed building relationships across many teams while helping people accomplish their goals. In a former role for Nordstrom, for instance, I helped run a project to revamp our internal ticketing tools, performing one-on-one meetings with every stakeholder in the technology organization to ensure the new system met their needs. Once I collected their requirements, I documented them, helped guide their delivery and followed up to ensure the launch was a success for all our users.

\vspace{\baselineskip}

I’m excited for the opportunity to apply at Gravity. I have a friend who works for the company, and I have heard from him that the culture is one of shared goals and appreciation for employees at every level. That level of community strongly matches what I seek in a place of employment. I value open communication, trust, and effective collaboration in my workplace, and I think I would be a great match for your team.

\vspace{\baselineskip}

Thank you for considering me. I hope to hear from you soon.

\vspace{\baselineskip}

Sincerely,

\vspace{\baselineskip}

Michael Shriver

\end{document}
