\documentclass[10pt,oneside]{article}
\usepackage{../Resume}

\begin{document}

\hfill\dte\today
\heading
\vspace{\baselineskip}
\vspace{\baselineskip}

Dear Hiring Manager.

\vspace{\baselineskip}

I am writing to apply for the Functional Analyst at DCHS. The course of my career so far has taken me from call-center based IT Support roles, to deskside Support roles. From these support roles, I eventually transitioned into Incident Management and response. Most recently, I have held a Systems Analyst role where I have done extensive data crunching and reporting to all levels of leadership at my organization. The parts of my job I have most consistently enjoyed and excelled at have always been the parts that involve helping filter and illuminate data in order to facilitate informed decision making.

\vspace{\baselineskip}

As I progressed in my career at Nordstrom, and showed an aptitude for using data to build processes that improve the efficiency and outcomes for my organization. I have gone from a front-line IT problem solver at the help desk, to writing and improving processes for the Help Desk, to eventually managing Incident Response for the entire IT organization. In my last role at Nordstrom, I was tasked with analyzing Incident and Problem Management data in order to provide the top leadership at the company with the information they needed to make critical business decisions around our IT projects. I produced weekly Tableau reports that were used by Directors, VPs and the CTO to drive down the frequency and impact of major IT incidents. I also worked directly with managers and product owners across the company, driving root-cause analysis and helping to find long-term solutions to problems that exist in the IT infrastructure. My passion in my day-to-day work life is building relationships with the people that I work with, and finding ways to collaboratively improve processes. I want to help people make better decisions. I believe these skills and experiences will allow me to be very successful in an analytical role, and I thrived knowing that I could enable sound decision-making through solid data.

\vspace{\baselineskip}

I’m excited for the opportunity to apply at King County. I am seeking a career where I can feel good about the work that I do, and where I can take satisfaction in serving the public's best interests. I value effective collaboration, curiosity and the ability to work together towards shared goals in my workplace, and I think I would be a great match for your team.

\vspace{\baselineskip}

Thank you for considering me. I hope to hear from you soon.

\vspace{\baselineskip}

Sincerely,

\vspace{\baselineskip}

Michael Shriver

\end{document}
