\documentclass[10pt,oneside]{article}
\usepackage{../Resume}

\begin{document}

\hfill\dte\today
\heading
\vspace{\baselineskip}
\vspace{\baselineskip}

Dear Kenny,

\vspace{\baselineskip}

I am writing to apply for the open Engineer position on the Developer Support Team. The course of my career so far has taken me from call-center based IT Support roles, to deskside Support roles. From these support roles, I eventually transitioned into Incident Management and response. Most recently, I have held a Systems Analyst role where I have done extensive data crunching and reporting to all levels of leadership at my organization. The parts of my job I have most consistently enjoyed and excelled at have always been the parts that involve complex problem solving and reducing friction that others have with technology.

\vspace{\baselineskip}

In past jobs, I’ve enjoyed outside-the-box problem solving to make my job, and the jobs of those around me, easier by writing and maintaining small tools and scripts. When I worked at the Service Desk, for instance, we lacked a unified hardware asset management tool. Seeing a gap I could fill, I built and maintained a powershell script that tracked the department’s workstations, laptops and other hardware. More recently, I wrote a small set of bash scripts to help my team automatically export Tableau reports to streamline our workflow. These were then included in a weekly Operations meeting that the CTO held. I am looking for a new area of expertise; but more than just a domain I can master, I wish to be a resource for others. The ideal skillset is one I can share and use to provide support for people so that they can perform their jobs more efficiently.

\vspace{\baselineskip}

I’m excited for the opportunity to apply at Nordstrom again. In the 8 years I worked at the company, I built many strong working relationships, and found a place that matches my drive and my values. I hope to rejoin the company. I have heard great things about your team, and I think I would be a great fit.

\vspace{\baselineskip}

Thank you for considering me. I hope to hear from you soon.

\vspace{\baselineskip}

Sincerely,

\vspace{\baselineskip}

Michael Shriver

\end{document}
